\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{array}     % for column customization
\usepackage{tabularx}  % for stretchable tables
\usepackage{algorithm}
\usepackage{algpseudocode}


\newcommand{\kfill}{\hrule height 1pt}

\title{The Mathematical Theory of Embodied Agentic AI}
\author{Daniel Drake}
\date{\today}

\begin{document}

\maketitle

\section{Symbols}
\kfill
.\\
Let the following hold:
\begin{itemize}
    \item $\mathbb{N}_K = \{1,2,3,...,K\}$
    \item $\mathbb{N}_K^0 = \{0\} \cup \mathbb{N}_K$
    \item $T \subseteq \mathbb{R}$
    \item $card(T) = N \in \mathbb{N}$
    \item $T = \{t_0,t_1,...,t_f\}$ where $(\forall j \in \mathbb{N}_{N-1}^0) (t_j < t_{j+1})$
    \item $T$ represent the times at which different events happen.
    \item $T_K = \{t_0,t_1,...,t_K\} \subseteq T$ represents the first K events.
\end{itemize}
\subsection{Sensors}
\kfill
.\\
\noindent Let the following hold:
\begin{itemize}
    \item $X = \prod_{j \in \mathbb{N}_K} X_j$ such that $(\forall j \in \mathbb{N}_K) (X_j \text{ is a TVS})$ 
    \item $(\forall x \in X)(x = (x_1,...,x_K))$
    \item $\pi_j : X \to X_j \pitchfork \pi_j(x) = x_j$
    \item $mem(type(x)) = \sum_{j \in \mathbb{N}_K} mem(type(\pi_j(x)))$
    \item $S$ represent a sensor.
    \item $S : T \to X$ 
    \item $D = S(T)$ represents all the data collected by the sensor.
    \item $D_k = S(T_k)$ represents the first k captures of the sensor. 
\end{itemize}
\subsubsection{Proposition}
\kfill
.\\
Given a finite amount of information, we can only draw a finite number of possible conclusions from it. 
\begin{table}[h]
\centering
\caption{16 Fundamental operations}
\begin{tabular}{c c c c c}
\toprule
A                      & 0 & 1 & 0 & 1 \\
B                      & 0 & 0 & 1 & 1 \\
\midrule
False                  & 0 & 0 & 0 & 0 \\
A AND B                & 0 & 0 & 0 & 1 \\
$A \not \Leftarrow B$  & 0 & 0 & 1 & 0 \\
B                      & 0 & 0 & 1 & 1 \\
$A \not \Rightarrow B$ & 0 & 1 & 0 & 0 \\
A                      & 0 & 1 & 0 & 1 \\
A XOR B                & 0 & 1 & 1 & 0 \\
A OR B                 & 0 & 1 & 1 & 1 \\
A NOR B                & 1 & 0 & 0 & 0 \\
A Equivalent B         & 1 & 0 & 0 & 1 \\
Not A                  & 1 & 0 & 1 & 0 \\
$A \Rightarrow B$      & 1 & 0 & 1 & 1 \\
Not B                  & 1 & 1 & 0 & 0 \\
$A \Leftarrow B$       & 1 & 1 & 0 & 1 \\
A NAND B               & 1 & 1 & 1 & 0 \\
True                   & 1 & 1 & 1 & 1 \\
\bottomrule
\end{tabular}
\end{table}
If we had two variables each of which can store 1 bit of information. 
Then there are $16$ possible manipulations of these variables and no more. 
It takes 4 bits of information to represent the operator associated with any of these manipulations. 
We are left with a problem: 
    Since we can know all of these operators: 
        How do we figure out which operators are useful?

In robotics we have this problem. 
We have sensor input and we need to transform that sensor input into packets of usable information. 
We often have high dimensional data with is to complicated to deal with on it's own.
From this we need to find ways to effectively go from the high dimensional data to a low dimensional data 
which is easier to deal with. 

In addition to this we have another problem. 
    A single frame of high dimensional data might not be enough information to appropriatly deal with that frame of data.
    We might need previous frames to come to the correct conclusion about the current frame. 
\newpage
\noindent A \textbf{Goal} is a function on which to optimize. \\
A \textbf{Strategy} is a solution to that optimization problem. \\
An \textbf{Implementation} is the collection of details on which the strategy is implemented. \\
A \textbf{Context} is the collection of details around a \{Goal, Strategy, Implementation\} problem.\\\\
\textbf{Example}:
\begin{itemize}
    \item $W,H \in \mathbb{N}$
    \item $I = [0,1]^{WxH}$
    \item $(x,y,z \in I)(x \not = z)$
    \item $f_z : I \rightarrow \mathbb{R}$
    \item $(\forall y \in I)(f_z(y)=||y-z||)$
    \item $M \in \mathbb{N}$
    \item Goal: Find any path: $\{x_t\}_{t\in\mathbb{N}_M^0}$ such that: as $t$ goes from $0 \rightarrow M$, $x_t$ goes from $x \rightarrow z$
    \item Strategy: \\
          $x_t = (\frac{t}{M}*z) + ((1-\frac{t}{M})*x)$ \\
          $f_z(x_0) = ||(\frac{0}{M}*z) + (1-\frac{0}{M})*x - z|| = ||x-z||$ \\
          $f_z(x_M) = ||(\frac{M}{M}*z) + (1-\frac{M}{M})*x|| = ||z-z|| = ||0|| = 0$
    \item Implementation:
        \begin{algorithmic}
        \State \texttt{size\_t} $t$ \Comment{Loop counter}
        \For{$t = 0$ \textbf{to} $M$}
            \State $x_t = \frac{t}{M} z + \left(1-\frac{t}{M}\right) x$
        \EndFor
        \end{algorithmic}
        \end{itemize}
        \newpage
        \textbf{Goals:}:
        \begin{itemize}
            \item Find an operator $T$ which creates value in an economic system. 
            \item Find an operator $T$ which turns a sequence of images $x_t$ into a 3d point cloud with identifications of the objects in the point clouds.
            \item Find an operator $T$ which turns a sequence of images $x_t$ into a the 6 dof localization of the camera. Roll, Pitch, Yaw, X, Y, Z.
            \item Find an operator $T$ which turns a sequence of images $x_t$ into a collection of sentences generated from words written in the scene. 
            \item Find an operator $T$ which passively listens for a wakeup word.
            \item Find an operator $T$ which actively listens for spoken word for a period of time.
            \item Find an operator $T$ which can turn text into text. 
            \item Find an operator $T$ which can turn text into sounds. 
            \item Find an operator $T$ which can turn the general neural network activity into sounds. 
            \item Find an operator $T$ which can generate new GSI problems involving 3d point clouds.
            \item Find an operator $T$ which can create the semblance of moods.
            \item Find an operator $T$ which tries to engage in natural conversation.
            \item Find an operator $T$ which tries to teach the droid language.
            \item Find an operator $T$ which can coordinate and direct which goals get executed.
            \item Find an operator $T$ which tries to translate verbal instruction into a GSI problem.
            \item Find an operator $T$ which executes artifical general intelligence.
            \item Find an operator $T$ which executes free will. 
            \item Find an operator $T$ which documents a GSI problems into UML. 
            \item Find an operator $T$ which allows the robot to explore and map a space. 
            \item Find an operator $T$ which allows the robot to climb on surfaces. 
            \item Find an operator $T$ which will allow the robot to follow another object. 
            \item Find an operator $T$ which filters a GSI problem through Issac Asimov's laws of robotics. 
            \item Find an operator $T$ which tune the robot's servos and walking motion through a sensor position solution. 
            \item Find an operator $T$ which calculates the forward kinematics. 
            \item Find an operator $T$ which calculates the inverse kinematics. 
            \item Find an operator $T$ which does laser reflection + camera information analysis. 
            \item Find an operator $T$ which does a power usage analysis. 
            \item Find an operator $T$ which recognizes animal behaviors. 
            \item Find an operator $T$ which allows the robot to dig. 
            \item Find an operator $T$ which identifies different materials. 
            \item Find an operator $T$ which can actively try to solve GSI problems. 
        \end{itemize}




\end{document}